### 2019-09-21 ch1_introduction/content.tex
update

Uncontrolled development of software tools without comprehensive benchmarking poses serious problems. 
For one, it slows down scientific progress. Every end-user needs to make a large commitment researching the domain in order to make an informed decision of which tool to use, or risk a higher incidence of false positive discoveries (either way, valuable resources are being wasted). It also negatively impacts the credibility of the field and discourages new users.

@@

\begin{itemize}
	\item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. Computational methods for trajectory inference from single-cell transcriptomics. European journal of immunology. 2016 Nov;46(11):2496-506.
	\item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. bioRxiv. 2016 Oct:079509.
	\item \textbf{Cannoodt R}, Ruyssinck J, Ramon J, De Preter K, Saeys Y. IncGraph: Incremental graphlet counting for topology optimisation. PloS one. 2018 Apr 26;13(4):e0195997.
  \item Saelens W *, \textbf{Cannoodt R} *, Todorov H, Saeys Y. A comparison of single-cell trajectory inference methods. Nature biotechnology. 2019 May;37(5):547.
  \item dyngen, submitted?
  \item dyno, submitted?
  \item scorpius, submitted?
  \item bred, submitted?
 \end{itemize}

@@

\subsection{Co-author publications}
\begin{itemize}
	\item Decock A, Ongenaert M, \textbf{Cannoodt R}, Verniers K, De Wilde B, Laureys G, Van Roy N, Berbegall AP, Bienertova-Vasku J, Bown N, Clément N. Methyl-CpG-binding domain sequencing reveals a prognostic methylation signature in neuroblastoma. Oncotarget. 2016 Jan 12;7(2):1960.
	\item Van Cauwenbergh C, Van Schil K, \textbf{Cannoodt R}, Bauwens M, Van Laethem T, De Jaegere S, Steyaert W, Sante T, Menten B, Leroy BP, Coppieters F. arrEYE: a customized platform for high-resolution copy number analysis of coding and noncoding regions of known and candidate retinal dystrophy genes and retinal noncoding RNAs. Genetics in Medicine. 2017 Apr;19(4):457.
	\item Claeys S, Denecker G, \textbf{Cannoodt R}, Kumps C, Durinck K, Speleman F, De Preter K. Early and late effects of pharmacological ALK inhibition on the neuroblastoma transcriptome. Oncotarget. 2017 Dec 5;8(63):106820.
	\item Depuydt P, Boeva V, Hocking TD, \textbf{Cannoodt R}, Ambros IM, Ambros PF, Asgharzadeh S, Attiyeh EF, Combaret V, Defferrari R, Fischer M. Genomic amplifications and distal 6q loss: novel markers for poor survival in high-risk neuroblastoma patients. JNCI: Journal of the National Cancer Institute. 2018 Mar 5;110(10):1084-93.
	\item Scott CL, T'Jonck W, \ldots, \textbf{Cannoodt R}, Saelens W \ldots, Guilliams M. The transcription factor ZEB2 is required to maintain the tissue-specific identities of macrophages. Immunity. 2018 Aug 21;49(2):312-25.
	\item Saelens W, \textbf{Cannoodt R}, Saeys Y. A comprehensive evaluation of module detection methods for gene expression data. Nature communications. 2018 Mar 15;9(1):1090.
	\item Todorov H, \textbf{Cannoodt R}, Saelens W, Saeys Y. Network Inference from Single-Cell Transcriptomic Data. In Gene Regulatory Networks 2019 (pp. 235-249). Humana Press, New York, NY..
	\item Van den Berge K, De Bezieux HR, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S, Clement L. Trajectory-based differential expression analysis for single-cell sequencing data. BioRxiv. 2019 Jan 1:623397.
	\item Weber LM, Saelens W, \textbf{Cannoodt R}, Soneson C, Hapfelmeier A, Gardner PP, Boulesteix AL, Saeys Y, Robinson MD. Essential guidelines for computational method benchmarking. Genome biology. 2019 Dec;20(1):125.
\end{itemize}

\mycomment{
	Submitted:\\
	RNA atlas,\\
	TRADE-seq: Trajectory-based differential expression analysis,\\
	SCENIC protocol
}

>>>>

Uncontrolled development of software tools without comprehensive benchmarking poses serious problems. 
For one, it slows down scientific progress. Every end-user needs to make a large commitment researching the domain in order to make an informed decision of which tool to use, or risk a higher incidence of false positive discoveries (either way, valuable resources are being wasted). In addition, it also negatively impacts the credibility of the field, thus discouraging potential users or researchers from entering.

@@

\begin{itemize}
  \item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. Computational methods for trajectory inference from single-cell transcriptomics. European journal of immunology. 2016 Nov;46(11):2496-506.
  \item \textbf{Cannoodt R}, Ruyssinck J, Ramon J, De Preter K, Saeys Y. IncGraph: Incremental graphlet counting for topology optimisation. PloS one. 2018 Apr 26;13(4):e0195997.
  \item Saelens W *, \textbf{Cannoodt R} *, Todorov H, Saeys Y. A comparison of single-cell trajectory inference methods. Nature biotechnology. 2019 May;37(5):547.
  \item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyngen: Simulating developing single cells. In preparation.
  \item \textbf{Cannoodt R}, Saelens W, Sichien D, Tavernier S, Janssens S, Guilliams M, Lambrecht B, De Preter K, Saeys Y. SCORPIUS: Fast, accurate, and robust single-cell pseudotime. In preparation.
  \item \textbf{Cannoodt R} *, Saelens W *, Saeys Y. dyno: A toolkit for inferring, visualising, and interpreting trajectories. In preparation.
  \item \textbf{Cannoodt R}, Saelens W, Saeys Y. bred: Inferring single cell regulatory networks. In preparation.
 \end{itemize}

@@

\subsection{Co-author publications}
\begin{itemize}
  \item Decock A, Ongenaert M, \textbf{Cannoodt R}, Verniers K, De Wilde B, Laureys G, Van Roy N, Berbegall AP, Bienertova-Vasku J, Bown N, Clément N. Methyl-CpG-binding domain sequencing reveals a prognostic methylation signature in neuroblastoma. Oncotarget. 2016 Jan 12;7(2):1960.
  \item Van Cauwenbergh C, Van Schil K, \textbf{Cannoodt R}, Bauwens M, Van Laethem T, De Jaegere S, Steyaert W, Sante T, Menten B, Leroy BP, Coppieters F. arrEYE: a customized platform for high-resolution copy number analysis of coding and noncoding regions of known and candidate retinal dystrophy genes and retinal noncoding RNAs. Genetics in Medicine. 2017 Apr;19(4):457.
  \item Claeys S, Denecker G, \textbf{Cannoodt R}, Kumps C, Durinck K, Speleman F, De Preter K. Early and late effects of pharmacological ALK inhibition on the neuroblastoma transcriptome. Oncotarget. 2017 Dec 5;8(63):106820.
  \item Depuydt P, Boeva V, Hocking TD, \textbf{Cannoodt R}, Ambros IM, Ambros PF, Asgharzadeh S, Attiyeh EF, Combaret V, Defferrari R, Fischer M. Genomic amplifications and distal 6q loss: novel markers for poor survival in high-risk neuroblastoma patients. JNCI: Journal of the National Cancer Institute. 2018 Mar 5;110(10):1084-93.
  \item Scott CL, T'Jonck W, \ldots, \textbf{Cannoodt R}, Saelens W \ldots, Guilliams M. The transcription factor ZEB2 is required to maintain the tissue-specific identities of macrophages. Immunity. 2018 Aug 21;49(2):312-25.
  \item Saelens W, \textbf{Cannoodt R}, Saeys Y. A comprehensive evaluation of module detection methods for gene expression data. Nature communications. 2018 Mar 15;9(1):1090.
  \item Todorov H, \textbf{Cannoodt R}, Saelens W, Saeys Y. Network Inference from Single-Cell Transcriptomic Data. In Gene Regulatory Networks 2019 (pp. 235-249). Humana Press, New York, NY..
  \item Van den Berge K, De Bezieux HR, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S, Clement L. Trajectory-based differential expression analysis for single-cell sequencing data. BioRxiv. 2019 Jan 1:623397.
  \item Weber LM, Saelens W, \textbf{Cannoodt R}, Soneson C, Hapfelmeier A, Gardner PP, Boulesteix AL, Saeys Y, Robinson MD. Essential guidelines for computational method benchmarking. Genome biology. 2019 Dec;20(1):125.
  \item Lorenzi L, \ldots, \textbf{Cannoodt R}, \ldots, Mestdagh P. The RNA-Atlas, a single nucleotide resolution map of the human transcriptome. In preparation.
  \item Van den Berge K, Roux de Bézieux H, Street K, Saelens W, \textbf{Cannoodt R}, Saeys Y, Dudoit S. Trajectory-based differential expression analysis. Submitted to Nature Communications.
  \item Van de Sande Bram, \ldots, \textbf{Cannoodt R}, \ldots, Saeys Y, Aerts S. A scalable SCENIC workflow for single-cell gene regulatory network analysis. Submitted to Nature Protocols.
\end{itemize}
